Fitting waggle dance models to waggle dance data

### 2022-04-05 analysis/fit_models_durations.Rmd
updated run through. Sometime the routine finds a weid pocket and the likelihood scores can stray out of bounds.

```{r, make-plots, message = FALSE, warning = FALSE}
# save the analysis results for all sites
save(all_sites, file = "results/site_fit_results.Rdata")

>>>>

```{r, make-plots, message = FALSE, warning = FALSE}
# save the analysis results for all sites
# save(all_sites, file = "results/site_fit_results.Rdata")
